\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
less than fixed

Irrespective of and additonal to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element. The \emph{context class} limits the constraint to individuals of a specific class. Depending on the constraining elements, a list of \emph{classes} can be provided, for example to determine the valid classes for a value or to define a class intersection to be used in a constraint. \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to. A typical example for a constraint with a right hand side list of properties would be R43, literal value comparision, where constraints like birthDate < deathDate can be expressed.

>>>>

Irrespective of and additonal to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element. The \emph{context class} limits the constraint to individuals of a specific class. Depending on the constraining elements, a list of \emph{classes} can be provided, for example to determine the valid classes for a value or to define a class intersection to be used in a constraint. \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to. A typical example for a constraint with a right hand side list of properties would be R43, literal value comparision, where constraints like birthDate $<$ deathDate can be expressed.
